---
title: "John's first R-Markdown presentation"
author: "John R Sullivan"
date: "December 2, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets
### High level sub heading
#### Lower Level subheading

- Bullet one
- Bullet two
- Bullet two and a 1/2

1. Numbered item A
2. Numbered Item B

## Slide with R Output

```{r cars, echo = TRUE,comment="",warning=FALSE,message=FALSE}
library(tidyverse)
summary(cars)
head(cars)

```

## Including a figure 

```{r hidden figures, echo = FALSE,comment="",fig.cap="My caption"}
plot(cars$speed,cars$dist,main="My cars plot",xlab="speed",ylab="dist")

```

## Slide with Plot

```{r pressure}
plot(pressure)
```

